---
title: "Balanced Training Set"
author: "Siyuan (Tom) Zhang"
date: "3/2/2022"
output: html_document
---

## Transform Data Into Indicator Format

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(broom)
library(jsonlite)
library(igraph)
library(purrr)
library(glmnet)
library(lubridate)
library(magrittr)

clash <- read_csv("sample/clash_sample_500k.csv", 
    col_types = cols(battleid = col_character(), 
        playertag = col_character(), battletime = col_datetime(format = "%Y-%m-%d %H:%M:%S"), 
        type = col_character(), isladdertournament = col_logical(), 
        arenaid = col_number(), arena = col_character(), 
        gamemodeid = col_number(), gamemode = col_character(), 
        deckselection = col_character(), 
        team = col_logical(), card = col_character(), 
        cardlevel = col_number(), clantag = col_character(), 
        startingtrophies = col_number(), 
        trophychange = col_number(), crowns = col_number(), 
        princesstower1hitpoints = col_number(), 
        princesstower2hitpoints = col_number(), 
        kingtowerhitpoints = col_number(), 
        boatbattleside = col_character(), 
        boatbattlewon = col_logical(), newboattowersdestroyed = col_number(), 
        prevboattowersdestroyed = col_number(), 
        remainingboattowers = col_number()))

clash <-
clash %>%
  mutate(card = str_replace(card, "^Fire Spirits$", "Fire Spirit")) %>%
  mutate(card = str_replace(card, "^Heal$", "Heal Spirit"))

clash <-
clash %>%
  filter(!str_starts(card, "(left)|(right)"))

# a matrix of card indicators
x <- model.matrix(~0 + card + cardlevel, model.frame(~ ., clash, na.action=na.pass))

# clean up col names
colnames(x) <- str_remove_all(colnames(x), "card")
colnames(x) <- str_replace_all(colnames(x), " ", "_")
colnames(x) <- str_replace_all(colnames(x), "-", "_")
colnames(x) <- str_replace_all(colnames(x), "\\.", "_")

# save a copy of just card indicators
card_indicators <- x[, -ncol(x)]

# ignore levels for now

# # transform card levels into the same structure of card indicators
# card_levels = sweep(x[,-ncol(x)], MARGIN = 1, STATS = x[,ncol(x)], FUN = "*")
# 
# # make col names for card levels
# colnames(card_levels) = paste(colnames(card_levels),"_Level",sep = "")

# create names for all card and card interaction terms to be used later
interactions <- labels(terms(~ .^2, data = x[1:10, -ncol(x)]))

rm(x)  # free up memory

# put all columns together
cr <-
  # cbind(card_indicators, card_levels) %>%
  card_indicators %>%
  as_tibble() %>%
  mutate(battleid = clash$battleid,
         playertag = clash$playertag,
         battlewon = clash$trophychange,
         battletime = clash$battletime) %>%
  group_by(battleid, playertag) %>%
  summarize_if(is.numeric, sum) %>%
  ungroup() %>%
  mutate(battlewon = if_else(battlewon >= 0 | is.na(battlewon), 1, 0))  # convert NA to 1

rm(clash)  # free up memory
rm(card_indicators)

cr
```

## Card Counts in Dataset

```{r}
tibble(card = names(cr[,3:(ncol(cr) - 1)]),
       count = colSums(cr[,3:(ncol(cr) - 1)])) %>%
  ggplot(., aes(x = count, y = card)) +
  geom_col()
```

## Balance Card Counts

Idea:
* Identify cards below the threshold: median
* Go through dataset by row
  - If current row contains enough above-median cards, remove it (or record row index in a list)
  - Update the two sets of cards separated by median threshold

```{r}
card_counts <- colSums(cr[3:(ncol(cr) - 1)])
median <- median(card_counts)
idx_to_remove <- NULL

for (i in 1:nrow(cr)) {
  row <- cr[i,]
  deck <- names(row)[which(row == 1)][-9]  # extract cards used in this row
  
  above_median_cards <- names(card_counts[card_counts > median])
  row_removed <- FALSE
  # if all 8 cards are have above-median counts
  if (sum(deck %in% above_median_cards) >= 8) {
    idx_to_remove <- c(idx_to_remove, i)
    row_removed <- TRUE
  }
  
  # update threshold
  if (row_removed) {
    # decrement card_counts by 1 for cards in current deck
    card_counts <- sapply(names(card_counts), function(card) {
      if (card %in% deck) {
        return(card_counts[[card]] - 1)
      } else {
        return(card_counts[[card]])
      }
    })
    # recalculate median
    median <- median(card_counts)
  }
}
```

## Undersampling

```{r}
cr1 <- cr[-idx_to_remove,]
```

## Outcome

```{r}
print(paste("Proportion of rows removed:", length(idx_to_remove) / nrow(cr)))
```

## Card Counts in Rebalanced Dataset

```{r}
tibble(card = names(cr1[,3:(ncol(cr1) - 1)]),
       count = colSums(cr1[,3:(ncol(cr1) - 1)])) %>%
  ggplot(., aes(x = count, y = card)) +
  geom_col()
```

## lasso part - same procedures

```{r}
cr_original <- cr
cr <- cr1



# get card name columns
cards <- names(cr)[3:(ncol(cr) - 1)]

# a place to store coefficients of every conditional model
# card = main card, term = all other cards, estimate = coef; exclude intercept
all_mods <- tibble(card = NA, term = NA, estimate = NA)

for (i in 1:length(cards)) {
  card <- cards[i]
  
  # subset data
  sub <- filter(cr, !!as.symbol(card) == 1)
  
  # response var and predictor matrix
  y <- sub$battlewon
  x <- data.matrix(sub[, cards[! cards %in% card]])  # all other cards
  
  # perform k-fold cross-validation to find optimal lambda value
  # note: this does not work if response is constant - problem with small datasets
  cv_model <- cv.glmnet(x, y, alpha = 1)
  
  # find optimal lambda value that minimizes test MSE
  best_lambda <- cv_model$lambda.min
  
  # find coefficients of best model
  mod <- glmnet(x, y, alpha = 1, lambda = best_lambda)
  
  tidy <-
    mod %>%
      tidy() %>%
      mutate(card = card) %>%
      select(card, term, estimate) %>%
      slice(-1) %>%
      slice_max(order_by = estimate, n=8)
  
  all_mods <- bind_rows(all_mods, tidy)
}

# keep only positive coefs
synergies <- 
  all_mods %>%
    filter(estimate > 0) %>%
    select(card, term)

# add back cards with no positive coefs
tmp <- tibble(card = cards, term = NA)
no_synergies <- anti_join(tmp, synergies, by = "card")  # get all cards not found in synergies df
# synergies <- bind_rows(synergies, no_synergies)



g <- graph_from_data_frame(synergies)
# plot(g)
# cliques(g, min = 2, max = 2)
clique_out <- cliques(g, min = 2, max = 2)



ints <-
clique_out %>%
  map(., function(clique) {
    vertices <- as_ids(clique)
    vertices <- vertices[vertices != "NA"]
    if (length(vertices) == 1) {  # an interaction needs at least 2 terms
      return(NULL)
    } else {
      return(paste(vertices, collapse = ":"))
    }
  }) %>%
  unlist()



f <- paste(
  "battlewon ~",
  paste(cards, collapse = " + "),
  " + ",
  paste(ints, collapse = " + ")
)

# sub <- cr %>% slice(1:50000)  # temporary solution to reduce wait time
t1 <- Sys.time()
mod_joint <- glm(f, data = cr, family = "binomial")
t2 <- Sys.time()

saveRDS(mod_joint, "mod_joint_b.rds")



mod_joint <- readRDS("mod_joint_b.rds")



mod_joint %>%
  tidy() %>%
  filter(str_detect(term, ":")) %>%
  filter(estimate > 0) %>%
  arrange(desc(estimate)) %>%
  mutate(  # calculate percentage of coef with p-value < 0.05
    significant = if_else(p.value < 0.05, 1, 0)
  ) %>%
  summarise(
    percent_significant_coef = sum(significant) / n()
  )
```








## TODO compare across seasons

Add in battle time

```{r}
clash <- read_csv("sample/clash_sample_2mm.csv", 
    col_types = cols(battleid = col_character(), 
        playertag = col_character(), battletime = col_datetime(format = "%Y-%m-%d %H:%M:%S"), 
        type = col_character(), isladdertournament = col_logical(), 
        arenaid = col_number(), arena = col_character(), 
        gamemodeid = col_number(), gamemode = col_character(), 
        deckselection = col_character(), 
        team = col_logical(), card = col_character(), 
        cardlevel = col_number(), clantag = col_character(), 
        startingtrophies = col_number(), 
        trophychange = col_number(), crowns = col_number(), 
        princesstower1hitpoints = col_number(), 
        princesstower2hitpoints = col_number(), 
        kingtowerhitpoints = col_number(), 
        boatbattleside = col_character(), 
        boatbattlewon = col_logical(), newboattowersdestroyed = col_number(), 
        prevboattowersdestroyed = col_number(), 
        remainingboattowers = col_number()))

clash <-
clash %>%
  mutate(card = str_replace(card, "^Fire Spirits$", "Fire Spirit")) %>%
  mutate(card = str_replace(card, "^Heal$", "Heal Spirit"))

clash <-
clash %>%
  filter(!str_starts(card, "(left)|(right)"))

# a matrix of card indicators
x <- model.matrix(~0 + card + cardlevel, model.frame(~ ., clash, na.action=na.pass))

# clean up col names
colnames(x) <- str_remove_all(colnames(x), "card")
colnames(x) <- str_replace_all(colnames(x), " ", "_")
colnames(x) <- str_replace_all(colnames(x), "-", "_")
colnames(x) <- str_replace_all(colnames(x), "\\.", "_")

# save a copy of just card indicators
card_indicators <- x[, -ncol(x)]

# ignore levels for now

# # transform card levels into the same structure of card indicators
# card_levels = sweep(x[,-ncol(x)], MARGIN = 1, STATS = x[,ncol(x)], FUN = "*")
# 
# # make col names for card levels
# colnames(card_levels) = paste(colnames(card_levels),"_Level",sep = "")

# create names for all card and card interaction terms to be used later
interactions <- labels(terms(~ .^2, data = x[1:10, -ncol(x)]))

rm(x)  # free up memory

# put all columns together
cr_time <-
  card_indicators %>%
  as_tibble() %>%
  mutate(battleid = clash$battleid,
         playertag = clash$playertag,
         battlewon = clash$trophychange,
         battletime = clash$battletime) %>%
  group_by(battleid, playertag, battletime) %>%
  summarize_if(is.numeric, sum) %>%
  ungroup() %>%
  mutate(battlewon = if_else(battlewon >= 0 | is.na(battlewon), 1, 0))

rm(clash)  # free up memory
rm(card_indicators)
```

Identify consecutive seasons with good amounts of data

```{r}
cr_time %>%
  mutate(year = year(battletime),
         month = month(battletime)) %>%
  unite("ym", year, month, sep = "-", remove = F) %>%
  select(year, month, ym) %>%
  group_by(ym) %>%
  summarise(
    n = n()
  ) %>%
  ungroup() %>%
  arrange(desc(n))
```

Subset those seasons

```{r}
cr_time <-
cr_time %>%
  mutate(year = year(battletime),
         month = month(battletime)) %>%
  unite("ym", year, month, sep = "-")
```

```{r}
cr_2019_6 <- filter(cr_time, ym == "2019-6") %>% select(-battletime, -ym)
cr_2019_7 <- filter(cr_time, ym == "2019-7") %>% select(-battletime, -ym)
cr_2019_8 <- filter(cr_time, ym == "2019-8") %>% select(-battletime, -ym)
cr_2019_9 <- filter(cr_time, ym == "2019-9") %>% select(-battletime, -ym)
cr_2019_10 <- filter(cr_time, ym == "2019-10") %>% select(-battletime, -ym)
cr_2019_11 <- filter(cr_time, ym == "2019-11") %>% select(-battletime, -ym)
cr_2019_12 <- filter(cr_time, ym == "2019-12") %>% select(-battletime, -ym)
```

For each season:
Fit conditional models -> get interaction terms -> fit joint model

```{r}
reduce <- function(cr) {
  card_counts <- colSums(cr[3:(ncol(cr) - 1)])
  median <- median(card_counts)
  idx_to_remove <- NULL
  
  for (i in 1:nrow(cr)) {
    row <- cr[i,]
    deck <- names(row)[which(row == 1)][-9]  # extract cards used in this row
    
    above_median_cards <- names(card_counts[card_counts > median])
    row_removed <- FALSE
    # if all 8 cards are have above-median counts
    if (sum(deck %in% above_median_cards) >= 8) {
      idx_to_remove <- c(idx_to_remove, i)
      row_removed <- TRUE
    }
    
    # update threshold
    if (row_removed) {
      # decrement card_counts by 1 for cards in current deck
      card_counts <- sapply(names(card_counts), function(card) {
        if (card %in% deck) {
          return(card_counts[[card]] - 1)
        } else {
          return(card_counts[[card]])
        }
      })
      # recalculate median
      median <- median(card_counts)
    }
  }
  
  
  
  cr1 <- cr[-idx_to_remove,]
  
  
  
  print(paste("Proportion of rows removed:", length(idx_to_remove) / nrow(cr)))
  
  
  
  cr_original <- cr
  cr <- cr1
  
  
  
  # get card name columns
  cards <- names(cr)[3:(ncol(cr) - 1)]
  
  # a place to store coefficients of every conditional model
  # card = main card, term = all other cards, estimate = coef; exclude intercept
  all_mods <- tibble(card = NA, term = NA, estimate = NA)
  
  for (i in 1:length(cards)) {
    card <- cards[i]
    
    # subset data
    sub <- filter(cr, !!as.symbol(card) == 1)
    
    # response var and predictor matrix
    y <- sub$battlewon
    x <- data.matrix(sub[, cards[! cards %in% card]])  # all other cards
    
    # perform k-fold cross-validation to find optimal lambda value
    # note: this does not work if response is constant - problem with small datasets
    cv_model <- cv.glmnet(x, y, alpha = 1)
    
    # find optimal lambda value that minimizes test MSE
    best_lambda <- cv_model$lambda.min
    
    # find coefficients of best model
    mod <- glmnet(x, y, alpha = 1, lambda = best_lambda)
    
    tidy <-
      mod %>%
        tidy() %>%
        mutate(card = card) %>%
        select(card, term, estimate) %>%
        slice(-1) %>%
        slice_max(order_by = estimate, n=8)
    
    all_mods <- bind_rows(all_mods, tidy)
  }
  
  # keep only positive coefs
  synergies <- 
    all_mods %>%
      filter(estimate > 0) %>%
      select(card, term)
  
  # add back cards with no positive coefs
  tmp <- tibble(card = cards, term = NA)
  no_synergies <- anti_join(tmp, synergies, by = "card")  # get all cards not found in synergies df
  # synergies <- bind_rows(synergies, no_synergies)
  
  
  
  g <- graph_from_data_frame(synergies)
  # plot(g)
  # cliques(g, min = 2, max = 2)
  clique_out <- cliques(g, min = 2, max = 2)
  
  
  
  ints <-
  clique_out %>%
    map(., function(clique) {
      vertices <- as_ids(clique)
      vertices <- vertices[vertices != "NA"]
      if (length(vertices) == 1) {  # an interaction needs at least 2 terms
        return(NULL)
      } else {
        return(paste(vertices, collapse = ":"))
      }
    }) %>%
    unlist()
  
  
  
  f <- paste(
    "battlewon ~",
    paste(cards, collapse = " + "),
    " + ",
    paste(ints, collapse = " + ")
  )
  
  # sub <- cr %>% slice(1:50000)  # temporary solution to reduce wait time
  t1 <- Sys.time()
  mod_joint <- glm(f, data = cr, family = "binomial")
  t2 <- Sys.time()
  
  
  
  mod_joint %>%
    tidy() %>%
    filter(str_detect(term, ":")) %>%
    filter(estimate > 0) %>%
    arrange(desc(estimate)) %>%
    mutate(  # calculate percentage of coef with p-value < 0.05
      significant = if_else(p.value < 0.05, 1, 0)
    ) %>%
    summarise(
      percent_significant_coef = sum(significant) / n()
    ) %>%
    use_series(percent_significant_coef) %>%
    print()
}
```

```{r}
for (i in 6:12) {
  print(paste0("cr_2019_", i))
  reduce(eval(parse(text = paste0("cr_2019_", i))))
}
```
