---
title: "Weighted Model"
author: "Siyuan (Tom) Zhang"
date: "3/9/2022"
output: html_document
---

## Transform Data Into Indicator Format

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(broom)
library(jsonlite)
library(igraph)
library(purrr)
library(glmnet)
library(lubridate)
library(magrittr)

clash <- read_csv("sample/clash_sample_500k.csv", 
    col_types = cols(battleid = col_character(), 
        playertag = col_character(), battletime = col_datetime(format = "%Y-%m-%d %H:%M:%S"), 
        type = col_character(), isladdertournament = col_logical(), 
        arenaid = col_number(), arena = col_character(), 
        gamemodeid = col_number(), gamemode = col_character(), 
        deckselection = col_character(), 
        team = col_logical(), card = col_character(), 
        cardlevel = col_number(), clantag = col_character(), 
        startingtrophies = col_number(), 
        trophychange = col_number(), crowns = col_number(), 
        princesstower1hitpoints = col_number(), 
        princesstower2hitpoints = col_number(), 
        kingtowerhitpoints = col_number(), 
        boatbattleside = col_character(), 
        boatbattlewon = col_logical(), newboattowersdestroyed = col_number(), 
        prevboattowersdestroyed = col_number(), 
        remainingboattowers = col_number()))

clash <-
clash %>%
  mutate(card = str_replace(card, "^Fire Spirits$", "Fire Spirit")) %>%
  mutate(card = str_replace(card, "^Heal$", "Heal Spirit"))

clash <-
clash %>%
  filter(!str_starts(card, "(left)|(right)"))

# a matrix of card indicators
x <- model.matrix(~0 + card + cardlevel, model.frame(~ ., clash, na.action=na.pass))

# clean up col names
colnames(x) <- str_remove_all(colnames(x), "card")
colnames(x) <- str_replace_all(colnames(x), " ", "_")
colnames(x) <- str_replace_all(colnames(x), "-", "_")
colnames(x) <- str_replace_all(colnames(x), "\\.", "_")

# save a copy of just card indicators
card_indicators <- x[, -ncol(x)]

# ignore levels for now

# # transform card levels into the same structure of card indicators
# card_levels = sweep(x[,-ncol(x)], MARGIN = 1, STATS = x[,ncol(x)], FUN = "*")
# 
# # make col names for card levels
# colnames(card_levels) = paste(colnames(card_levels),"_Level",sep = "")

# create names for all card and card interaction terms to be used later
interactions <- labels(terms(~ .^2, data = x[1:10, -ncol(x)]))

rm(x)  # free up memory

# put all columns together
cr <-
  # cbind(card_indicators, card_levels) %>%
  card_indicators %>%
  as_tibble() %>%
  mutate(battleid = clash$battleid,
         playertag = clash$playertag,
         battlewon = clash$trophychange,
         battletime = clash$battletime) %>%
  group_by(battleid, playertag) %>%
  summarize_if(is.numeric, sum) %>%
  ungroup() %>%
  mutate(battlewon = if_else(battlewon >= 0 | is.na(battlewon), 1, 0))  # convert NA to 1

rm(clash)  # free up memory
rm(card_indicators)

cr
```

## Card Counts in Dataset

```{r}
cards_matrix <- cr[,3:(ncol(cr) - 1)]

tibble(card = names(cards_matrix),
       count = colSums(cards_matrix)) %>%
  ggplot(., aes(x = count, y = card)) +
  geom_col()
```

## Card Weights

card weight = 1 / card count

```{r}
card_weights <-
tibble(card = names(cards_matrix),
       count = colSums(cards_matrix)) %>%
  mutate(weight = 1 / count) %>%
  select(card, weight)

card_weights
```

## Training Data Weights

Each row (match) in training dataset gets a weight: match weight = sqrt(sum(weights of cards used in match)) Match weights will be stored as row names.

```{r warning=FALSE}
# runtime ~ 15 min

row_names <- character(nrow(cr))

for (i in 1:nrow(cr)) {
  row <- cr[i,]
  deck <- names(row)[which(row == 1)][-9]  # extract cards used in this row
  match_weight <- card_weights %>%
    filter(card %in% deck) %>%
    use_series(weight) %>%
    sum() %>%
    sqrt()
  row_names[i] <- paste(i, round(match_weight, 4), sep = ",")
}

rownames(cr) <- row_names
```

## lasso part - same procedures, but specify weight option in glmnet()

***Also, joint model should use glmnet(), not glm()***

```{r}
# get card name columns
cards <- names(cr)[3:(ncol(cr) - 1)]

# a place to store coefficients of every conditional model
# card = main card, term = all other cards, estimate = coef; exclude intercept
all_mods <- tibble(card = NA, term = NA, estimate = NA)

for (i in 1:length(cards)) {
  card <- cards[i]
  
  # subset data
  sub <- filter(cr, !!as.symbol(card) == 1)
  
  # response var and predictor matrix
  y <- sub$battlewon
  x <- data.matrix(sub[, cards[! cards %in% card]])  # all other cards
  
  # get weights
  weights <- str_remove(rownames(sub), ".*,") %>% as.numeric()
  
  # perform k-fold cross-validation to find optimal lambda value
  # note: this does not work if response is constant - problem with small datasets
  cv_model <- cv.glmnet(x, y, alpha = 1, weights = weights)
  
  # find optimal lambda value that minimizes test MSE
  best_lambda <- cv_model$lambda.min
  
  # find coefficients of best model
  mod <- glmnet(x, y, alpha = 1, lambda = best_lambda, weights = weights)
  
  tidy <-
    mod %>%
      tidy() %>%
      mutate(card = card) %>%
      select(card, term, estimate) %>%
      slice(-1) %>%
      slice_max(order_by = estimate, n=8)
  
  all_mods <- bind_rows(all_mods, tidy)
}

# keep only positive coefs
synergies <- 
  all_mods %>%
    filter(estimate > 0) %>%
    select(card, term)

# add back cards with no positive coefs
tmp <- tibble(card = cards, term = NA)
no_synergies <- anti_join(tmp, synergies, by = "card")  # get all cards not found in synergies df
# synergies <- bind_rows(synergies, no_synergies)



g <- graph_from_data_frame(synergies)
clique_out <- cliques(g, min = 2, max = 2)



ints <-
clique_out %>%
  map(., function(clique) {
    vertices <- as_ids(clique)
    vertices <- vertices[vertices != "NA"]
    if (length(vertices) == 1) {  # an interaction needs at least 2 terms
      return(NULL)
    } else {
      return(paste(vertices, collapse = ":"))
    }
  }) %>%
  unlist()



f <- paste(
  "battlewon ~",
  paste(cards, collapse = " + "),
  " + ",
  paste(ints, collapse = " + ")
)
```

Joint model - glmnet()

```{r}
t1 <- Sys.time()



# make predictor matrix
y <- cr$battlewon
df <- cr[,-c(1, 2)]  # keep cards & battlewon (response)
x <- model.matrix(as.formula(f), data = df)[,-1]  # x matrix for glmnet()

# get weights
weights <- str_remove(rownames(cr), ".*,") %>% as.numeric()

# perform k-fold cross-validation to find optimal lambda value
cv_model <- cv.glmnet(x, y, alpha = 1, weights = weights)

# find optimal lambda value that minimizes test MSE
best_lambda <- cv_model$lambda.min

# find coefficients of best model
mod_joint <- glmnet(x, y, alpha = 1, lambda = best_lambda, weights = weights)



t2 <- Sys.time()

saveRDS(mod_joint, "mod_joint_w.rds")
```

## Compare original joint model to weighted model

```{r}
mod_joint_o <- readRDS("mod_joint.rds")
mod_joint_w <- readRDS("mod_joint_w.rds")
```

Percentage of zeroed out predictors in both joint models

```{r}
mod_joint_o %>%
  tidy() %>%
  filter(str_detect(term, ":")) %>%
  mutate(zero = if_else(abs(estimate) < 0.05, 1, 0)) %>%
  summarise(percent_zero = sum(zero) / n())
```

```{r}
mod_joint_w %>%
  tidy() %>%
  filter(str_detect(term, ":")) %>%
  mutate(zero = if_else(abs(estimate) < 0.05, 1, 0)) %>%
  summarise(percent_zero = sum(zero) / n())
```

```{r}
mod_joint_o %>%
  tidy() %>%
  ggplot(., aes(x = estimate)) +
  geom_histogram() +
  scale_x_continuous(limits = c(-0.05, 0.05))
```


```{r}
mod_joint_w %>%
  tidy() %>%
  ggplot(., aes(x = estimate)) +
  geom_histogram() +
  scale_x_continuous(limits = c(-0.05, 0.05))
```

